---
title: "Regression Analysis Lab: Foot_V_Height"
author: "Harris Rodis"
date: "4/2/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Loading Data
Using the data included in the india_foot_height.dat file. First column corresponds to Feet height (in cm) and the second to total Height (in cm) of a sample of Indian people.
```{r}
india_foot_height <- read.table("india_foot_height.dat")
names(india_foot_height)[1:2] <- c("Feet", "Height")
```

## Plotting Data
By creating a scatter plot of dependent variable "Height" and the indipendent variable "Feet" we observe a positive relation between these.
- The relation does not depend on the units of measure of the variables (changes in the "density" of axis does not change the relation)
- This relation holds even we reverse the plot's axis (by making Feet the dependent variable)
- If we square or take the log of one of our variables, the relation appears to change.
```{r}
plot(india_foot_height$Feet, india_foot_height$Height)
```

## Calculating r
The value 0.578 of r for out sample indicate a positive linear relation of our variables.
- We perform a t-test with H0: ρ = 0 and H1: ρ != 0.
- Based on the resulted p-value and confidence interval we can reject the H0 hypothesis.
```{r}
cor(india_foot_height$Feet, india_foot_height$Height)
cor.test(india_foot_height$Feet, india_foot_height$Height)
```
